Paper Figures and Data

### 2020-08-06 Microscopy Data Clean.Rmd
figures 3 and 6 black and white

#ok so I am going to try to do this...I can't do bar graphs because the width of the bars is too thin to be able to be seen by the viewer, so I am doing points
#I also want to do mono and co pointing to opposite sides, but I haven't been able to do it with recode, so I'll manually do it.
cleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))#Combine aggregates from all 3 samples
cleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
#However, one thing I want to try is to have different aggregate cutoffs... have 5 um bins up to 100um and then have the rest of the bins at 100 um3, so..
only5Hist<- cleanHist.5 %>% filter (max<=100)
only100Hist<- cleanHist.100 %>% filter (max>100)
bin5and100Hist<-bind_rows(only5Hist,only100Hist)

@@

#this is the summary beacuse I dont like further analyzing data after summarizing shit, so mutate at the top follows 
hist.plank.Agg.Sumary<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",
                        max>5 ~ "Aggregate")) %>% ungroup() %>% 
  group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
#now I have to do some t-tests, since I used the same cultures for mono and co for each replicate, paired t-tests are allowed.
##### 
#I know this sucks, but it's 1 AM so idgaf
SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)
SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)

@@

hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>%
  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation))

@@

```
```{r Aggregate histograms logarithmic bins}
#Now I need to do histograms with bins in a log scale, but for this I want to use the raw data that includes biomass per bin and density.
#let's start by revisiting the original data set and just filter one sample to simplify things:
hist.5.rep1<-hist.5 %>% filter(Sample == "rep1"&Condition == "Pa Mono"&Strain=="PA14mut")
hist.5.rep1.logBins<-hist.5.rep1 %>% 
  mutate(LogBin = case_when(max <= 10 ~ 10,
                        max<= 100    ~ 100,
                        max<= 1000   ~ 1000,
                        max<= 10000  ~ 10000,
                        max<= 100000 ~ 100000,
                        max > 100000 ~ 1000000)) %>% 
  group_by(LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
#Now this is the real case
hist.5.LogBin<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
  mutate(LogBin = case_when(max <= 10 ~ 10,
                        max<= 100    ~ 100,
                        max<= 1000   ~ 1000,
                        max<= 10000  ~ 10000,
                        max<= 100000 ~ 100000,
                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
  group_by(Species, Sample,Condition,Strain,LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))

@@

PlotFreqLogBin<-function(strain, species,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain & Species == species)
  ggplot()+
    geom_col(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  fill =Sample ),size=4)+
    #geom_point(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  shape =Sample ),size=4)+
    geom_label(data = df %>% filter(Sample == "rep1"),aes(x=as.factor(LogBin),y=1, label =round(BiomassLogBin*100,digits=1), color = "rep1"),size=4)+
    geom_label(data = df%>% filter(Sample == "rep2"),aes(x=as.factor(LogBin),y=.325, label =round(BiomassLogBin[Sample=="rep2"]*100,digits=1), color = "rep2"),size=4)+
    geom_label(data = df%>% filter(Sample == "rep3"),aes(x=as.factor(LogBin),y=.1, label =round(BiomassLogBin[Sample=="rep3"]*100,digits=1), color = "rep3"),size=4)+
    labs(title = titulo)+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~ConditionNew)+
    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotFreqLogBin("PA14wt", "Sa", "Sa WT")
PlotFreqLogBin("PA14wt", "Pa", "Pa WT")
PlotFreqLogBin("PA14mut", "Sa", "Sa pqsL")
PlotFreqLogBin("PA14mut", "Pa", "Pa pqsL")

>>>>

#ok so I am going to try to do this...I can't do bar graphs because the width of the bars is too thin to be able to be seen by the viewer, so I am doing points
#I also want to do mono and co pointing to opposite sides, but I haven't been able to do it with recode, so I'll manually do it.
cleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))#Combine aggregates from all 3 samples
meancleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(MeanFrequency = mean(frequency))#mean aggregates from all 3 samples
cleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
meancleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(MeanFrequency = mean(frequency))
#However, one thing I want to try is to have different aggregate cutoffs... have 5 um bins up to 100um and then have the rest of the bins at 100 um3, so..
only5Hist<- cleanHist.5 %>% filter (max<=100)
only100Hist<- cleanHist.100 %>% filter (max>100)
bin5and100Hist<-bind_rows(only5Hist,only100Hist)

meanOnly5Hist<- meancleanHist.5 %>% filter (max<=100)
meanOnly100Hist<- meancleanHist.100 %>% filter (max>100)
meanBin5and100Hist<-bind_rows(meanOnly5Hist,meanOnly100Hist)

@@

#this is the summary beacuse I dont like further analyzing data after summarizing shit, so mutate at the top follows 
hist.plank.Agg.Sumary<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",
                        max>5 ~ "Aggregate")) %>% ungroup() %>% 
  group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))

#now I have to do some t-tests, since I used the same cultures for mono and co for each replicate, paired t-tests are allowed.
##### 
#I know this sucks, but it's 1 AM so idgaf
SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)
SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)

@@

hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>%
  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation) )

@@

```{r Aggregate histograms logarithmic bins, Figures 3 and 6}
#Now I need to do histograms with bins in a log scale, but for this I want to use the raw data that includes biomass per bin and density.
#let's start by revisiting the original data set and just filter one sample to simplify things:
#####
hist.5.rep1<-hist.5 %>% filter(Sample == "rep1"&Condition == "Pa Mono"&Strain=="PA14mut")
hist.5.rep1.logBins<-hist.5.rep1 %>% 
  mutate(LogBin = case_when(max <= 10 ~ 10,
                        max<= 100    ~ 100,
                        max<= 1000   ~ 1000,
                        max<= 10000  ~ 10000,
                        max<= 100000 ~ 100000,
                        max > 100000 ~ 1000000)) %>% 
  group_by(LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
#Now this is the real case
hist.5.LogBin<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
  mutate(LogBin = case_when(max <= 10 ~ 10,
                        max<= 100    ~ 100,
                        max<= 1000   ~ 1000,
                        max<= 10000  ~ 10000,
                        max<= 100000 ~ 100000,
                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
  group_by(Species, Sample,Condition,Strain,LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))

@@

PlotFreqLogBin<-function(strain, species,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain & Species == species)
  ggplot()+
    geom_col(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  fill =Sample ),size=4)+
    #geom_point(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  shape =Sample ),size=4)+
    geom_label(data = df %>% filter(Sample == "rep1"),aes(x=as.factor(LogBin),y=1, label =round(BiomassLogBin[Sample=="rep1"]*100,digits=1), color = "rep1"),size=4)+
    geom_label(data = df%>% filter(Sample == "rep2"),aes(x=as.factor(LogBin),y=.325, label =round(BiomassLogBin[Sample=="rep2"]*100,digits=1), color = "rep2"),size=4)+
    geom_label(data = df%>% filter(Sample == "rep3"),aes(x=as.factor(LogBin),y=.1, label =round(BiomassLogBin[Sample=="rep3"]*100,digits=1), color = "rep3"),size=4)+
    labs(title = titulo)+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~ConditionNew)+
    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
 #old stuff
#####

#New code as of 8-5-20: report mean frequencies and density across samples, instead of per sample.
hist.5.LogBinSummarize<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
  mutate(LogBin = case_when(max <= 10 ~ "(5, 10]",
                        max<= 100    ~ "(10, 100]",
                        max > 100 ~ paste0("(100, ",bquote("\U221E"), ")"))) %>% ungroup() %>% 
  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density)) %>% 
  ungroup() %>% group_by(Species, Condition,ConditionNew,Strain,LogBin) %>% summarise(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
                                                                                      MeanBiomassLogBin = mean(BiomassLogBin), SEBiomassLogBin = std.error(BiomassLogBin),
                                                                                      MeanDensityLogBin = mean(DensityLogBin),SEDensityLogBin = std.error(DensityLogBin)) 
hist.5.LogBinSummarize$LogBin<-as.factor(hist.5.LogBinSummarize$LogBin)
hist.5.LogBinSummarize$LogBin <- factor(hist.5.LogBinSummarize$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
hist.5.LogBinSummarize$Species <- factor(hist.5.LogBinSummarize$Species, levels = c("Pa", "Sa"),
                  labels = c('P. aeruginosa','S. aureus'))

PlotFreqLogBin<-function(strain,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanFrequencyLogBin,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=MeanFrequencyLogBin-SEFrequencyLogBin, ymax = MeanFrequencyLogBin+SEFrequencyLogBin, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
    #labs(title = titulo)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~Species)+
    labs(fill = "Condition",y = "Mean number of aggregates per Bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_fill_grey()+
    theme_cowplot(12)+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
}

PlotFreqLogBin("PA14wt", "WT")
PlotFreqLogBin("PA14mut", "pqsL")

PlotDensityLogBin<-function(strain,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
    #labs(title = titulo)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~Species)+
    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_fill_grey()+
    theme_cowplot(12)+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
}
PlotDensityLogBin("PA14wt", "WT")
PlotDensityLogBin("PA14mut", "pqsL")
```

### 2020-08-06 Paper Figures/Paper figures Scipts.Rmd
figures 3 and 6 black and white

    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
    prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
                      align='vh',labels = c("Mixed", "Static"),hjust = c(-3, -3.8),nrow = 1)
    plot_grid(prow,legend,rel_widths = c(3, .4))
    }
#Graph logs
GraphGrowthCurveLog1(PA14Data,PA14DataStats)
```
Figures 2 and 5 are on document : "Staph killing assays.Rmd"

>>>>

    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
    prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
                      align='vh',labels = c("Mixed", "Static"),hjust = c(-3, -3.8),nrow = 1)
    plot_grid(prow,legend,rel_widths = c(3, .4))
    }
#Graph logs
GraphGrowthCurveLog1(PA14Data,PA14DataStats)
```
Figures 2 and 5 are on document : "Staph killing assays.Rmd"
```{r code Figures 3 and 6}
hist.5.LogBinSummarize<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
  mutate(LogBin = case_when(max <= 10 ~ "(5, 10]",
                        max<= 100    ~ "(10, 100]",
                        max > 100 ~ paste0("(100, ",bquote("\U221E"), ")"))) %>% ungroup() %>% 
  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density)) %>% 
  ungroup() %>% group_by(Species, Condition,ConditionNew,Strain,LogBin) %>% summarise(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
                                                                                      MeanBiomassLogBin = mean(BiomassLogBin), SEBiomassLogBin = std.error(BiomassLogBin),
                                                                                      MeanDensityLogBin = mean(DensityLogBin),SEDensityLogBin = std.error(DensityLogBin)) 
hist.5.LogBinSummarize$LogBin<-as.factor(hist.5.LogBinSummarize$LogBin)
hist.5.LogBinSummarize$LogBin <- factor(hist.5.LogBinSummarize$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
hist.5.LogBinSummarize$Species <- factor(hist.5.LogBinSummarize$Species, levels = c("Pa", "Sa"),
                  labels = c('P. aeruginosa','S. aureus'))

PlotFreqLogBin<-function(strain,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanFrequencyLogBin,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=MeanFrequencyLogBin-SEFrequencyLogBin, ymax = MeanFrequencyLogBin+SEFrequencyLogBin, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
    #labs(title = titulo)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~Species)+
    labs(fill = "Condition",y = "Mean number of aggregates per Bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_fill_grey()+
    theme_cowplot(12)+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
}

PlotFreqLogBin("PA14wt", "WT")
PlotFreqLogBin("PA14mut", "pqsL")

PlotDensityLogBin<-function(strain,titulo){
  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
    #labs(title = titulo)+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~Species)+
    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_fill_grey()+
    theme_cowplot(12)+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
}
PlotDensityLogBin("PA14wt", "WT")
PlotDensityLogBin("PA14mut", "pqsL")
